Equalizer Programming Guide

### 2008-12-08 Developer/ProgrammingGuide/paper.tex
Programming Guide: updates based on print version
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{15cm}
  {\Large\sffamily The official reference for creating parallel,
    scalable OpenGL\texttrademark\ applications with the Equalizer
    parallel rendering framework}\\\vspace{1cm}
  Version 1.4 for Equalizer 0.6\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    \hline
  \end{tabularx}}
\clearpage

@@

\begin{wrapfigure}{r}{.382\textwidth}
  \includegraphics[width=.382\textwidth]{images/statistics.png}
  {\caption{\small\label{fStatistics}Statistics for a two-node 2D compound}}
\end{wrapfigure}
Statistics are enabled per entity using an attribute hint. The hint
determines how precise the gathered statistics are. When set to
\textsf{fastest}, the per-frame clock is sampled directly when the event
occurs. When set to \textsf{nicest}, all OpenGL commands will be
finished before sampling the event. This incurs a performance penalty,
but gives more correct results. The default setting is fastest in
release builds, and nicest in debug builds.

>>>>

\date{
  \vspace{15cm}
  {\Large\sffamily The official reference for creating parallel,
    scalable OpenGL\texttrademark\ applications with the Equalizer
    parallel rendering framework}\\\vspace{1cm}
  Version 1.5.1 for Equalizer 0.6+svn\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
\listoffigures
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.5.1   & Dec 08, 2008 & Minor updates based on the print version\\
    \hline
  \end{tabularx}}
\clearpage

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/statistics.png}
  {\caption{\small\label{fStatistics}Statistics for a two-node 2D compound}}
\end{wrapfigure}
Statistics are enabled per entity using an attribute hint. The hint
determines how precise the gathered statistics are. When set to
\textsf{fastest}, the per-frame clock is sampled directly when the event
occurs. When set to \textsf{nicest}, all OpenGL commands will be
finished before sampling the event. This incurs a performance penalty,
but gives more correct results. The default setting is fastest in
release builds, and nicest in debug builds.
